---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dfuzz

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/manyfold)](https://CRAN.R-project.org/package=manyfold)
<!-- badges: end -->

The goal of __{manyfold}__ is to help you turns columns from your `data.frame` or `tibble` into a nested list which can be displayed as a tree like structure.

This package is __highly experimental__ and only contain a single function for now.

It is build around a single dependency: [__{data.tree}__](https://github.com/gluc/data.tree), and it is possible to use the full power of the functions from this excellent package on the output created by __{manyfold}__.


## Installation

You can install this package using __{remotes}__ (or __{devtools}__):

```r
remotes::install_github("courtiol/manyfold")
```

## Example

```{r example}
library(manyfold)

## Create a toy dataset:
 table <- data.frame(country = c("France", "France", "France", "France",
                                 "Spain", "Spain"),
                     region = c("Herault", "Herault", "Aude", "Paris",
                                "Catalonia", "Andalusia"),
                     city = c("Montpellier", "Montpellier", "Narbonne", "Paris",
                              "Barcelona", "Sevilla"))

 table

## Manyfold without specifying columns (takes them all in the order they come):
 manyfold(table)

## Manyfold with column specification:
 manyfold(table, "country", "region", "city")

## The order of the columns matters:
 manyfold(table, "region", "city", "country")

## Another way for displaying counts:
 print(manyfold(table, "country", "region", "city", count = FALSE), "N")
```

## Help \& feedbacks wanted!

If you find that this package is an idea worth pursuing, please let me know.
Developing is always more fun when it becomes a collaborative work.
So please also email me (or leave an issue) if you want to get involved!
